From heartbeat to data -- Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-09-24 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
Format Sachen

\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{caption}
\usepackage{tablefootnote}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{geometry}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
  \label{fig.1}
\end{figure}

@@

Each participant came to the lab for a period of approximately two hours
in total, and each participant underwent the same phases (see Fig. 2):
In the \emph{pre-teaching phase}, the experimenter welcomed the
participants and helped them put on the fitness tracker. This was
followed by a warm-up session to familiarize the participants with the
laboratory setting and the class. This phase took about 10-15 minutes
and participants spent this time mostly standing or slowly walking
around. During the \emph{teaching phase}, the participants held their
self-prepared micro-teaching unit to a class of three trained actors who
performed nine, potentially disruptive, classroom events (e.g., chatting
with a neighbor, heckling, looking at the phone; see Table \#\# in the
supplementary material for an overview and categorization of all events;
and Fig\#\# in the supplementary material for a depiction of the
laboratory setting of the micro-teaching unit). The topic and class
level of the teaching unit could be freely chosen by the teachers with
the only requirement that the unit had to be an introductory lesson, and
had to consist of supervised individual work and / or frontal teaching.
The micro-teaching unit lasted about 15-20 minutes. Participants spent
this time mostly standing or slowly walking around. While teaching,
participants wore eye-tracking glasses, and their lesson was
video-recorded. After having completed the micro-teaching unit, in the
\emph{post-teaching phase}, participants filled in questionnaires for
approximately 10-15 minutes: a brief computer-based survey of
sociodemographic data (e.g., teaching experience, gender, studied school
type, studied school subjects, extracurricular teaching activities), and
a short knowledge test that was irrelevant to the present study. In the
\emph{interview phase},

\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \label{fig.2}
\end{wrapfigure}

@@

@@

Means, standard deviations, and range of teachers' unstandardized and
standardized HR for the entire study period, and for the five intervals,
are shown in Table 1. Fig. 3 a. and b. display the unstandardized and
standardized HR trends, respectively, over the course of the entire
study period. HR initially increased, peaked, and then decreased, with
the unstandardized and standardized HR graphs showing high similarity.
Thus, for all further analyses, we used participants' standardized HR
values.

\begin{table}[ht]
    \centering
    \begin{tabularx}{\textwidth}{lXXXXX}
        \toprule
        Interval & \textit{M} HR & \textit{SD} HR & Min & Max \\
        \midrule
        Overall Course of 2h & 90.09/0.04\footnotemark[9] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
        Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
        Teaching interval ($I_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
        Post-teaching interval ($I_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
        Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[10]/-2.68 & 120/2.96 \\
        \bottomrule
    \end{tabularx}
    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
    \label{tab_1}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
  \label{fig.3}
\end{figure}

\newpage

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
  \caption{Distribution of the standardized heart rate means in the five intervals}
  \label{fig.4}
\end{figure}

@@

@@

\begin{table}[ht]
    \centering
    \begin{tabularx}{\textwidth}{lccccc}
        \toprule
        Variable & Pre-teaching & Teaching & Post-teaching & Interview & End \\
        & interval & interval & interval & interval & interval \\
        \midrule
        Teaching Experience & $- .17/ - .27^*$ & .11/-.02 & $- .04/-.03$ & $.24^*/-.20$ & .04/.11 \\
        Disruption Appraisal & $- .01/.16$ & $- .20/.08$ & .20/$- .14$ & $- .13/.01$ & .04/.12 \\
        Confidence Appraisal & $- .10/ - .18$ & .06/.09 & .04/$- .03$ & .09/$- .19$ & $- .07/.13$ \\
        \bottomrule \\
          Note. * $p < .05$.
    \end{tabularx}
    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
    \label{tab_3}
\end{table}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
  \label{fig.a1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
  \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \label{fig.a2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
  \caption{Preparation Phase}
  \label{fig.a3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \caption{Teaching Phase}
  \label{fig.a4}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
  \caption{Post-Teaching Phase}
  \label{fig.a5}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
  \caption{Interview Phase}
  \label{fig.a6}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
  \caption{End Phase}
  \label{fig.a7}
\end{figure}

>>>>

\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{caption}
\usepackage{tablefootnote}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{geometry}
\usepackage{caption}

@@

\captionsetup[figure]{
    labelfont=bf,         % Figure label bold (not italic)
    parskip=12pt,
    labelsep=newline,      % Period after Figure label
    textfont=it,          % Italic font for the caption text
    font=small,           % Smaller font size for APA style
    justification=justified, % Left-justified captions, as per APA guidelines
    singlelinecheck=false % Avoid centering if the caption is single-line
}

\captionsetup[table]{
    labelfont=bf,         % Figure label bold (not italic)
    parskip=12pt,
    labelsep=newline,      % Period after Figure label
    textfont=it,          % Italic font for the caption text
    font=small,           % Smaller font size for APA style
    justification=justified, % Left-justified captions, as per APA guidelines
    singlelinecheck=false % Avoid centering if the caption is single-line
}

\begin{figure}[htbp]
  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
  \centering
  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
  \label{fig.1}
\end{figure}

@@

Each participant came to the lab for a period of approximately two hours
in total, and each participant underwent the same phases (see Fig. 2):
In the \emph{pre-teaching phase}, the experimenter welcomed the
participants and helped them put on the fitness tracker. This was
followed by a warm-up session to familiarize the participants with the
laboratory setting and the class. This phase took about 10-15 minutes
and participants spent this time mostly standing or slowly walking
around. During the \emph{teaching phase}, the participants held their
self-prepared micro-teaching unit to a class of three trained actors who
performed nine, potentially disruptive, classroom events (e.g., chatting
with a neighbor, heckling, looking at the phone; see Table \#\# in the
supplementary material for an overview and categorization of all events;
and Figure \ref{fig.a2} in the supplementary material for a depiction of
the laboratory setting of the micro-teaching unit). The topic and class
level of the teaching unit could be freely chosen by the teachers with
the only requirement that the unit had to be an introductory lesson, and
had to consist of supervised individual work and / or frontal teaching.
The micro-teaching unit lasted about 15-20 minutes. Participants spent
this time mostly standing or slowly walking around. While teaching,
participants wore eye-tracking glasses, and their lesson was
video-recorded. After having completed the micro-teaching unit, in the
\emph{post-teaching phase}, participants filled in questionnaires for
approximately 10-15 minutes: a brief computer-based survey of
sociodemographic data (e.g., teaching experience, gender, studied school
type, studied school subjects, extracurricular teaching activities), and
a short knowledge test that was irrelevant to the present study. In the
\emph{interview phase},

\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
  \label{fig.2}
\end{wrapfigure}

@@

\begin{table}[ht]
    \centering
    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
    \begin{tabularx}{\textwidth}{lXXXXX}
        \toprule
        Interval & \textit{M} HR & \textit{SD} HR & Min & Max \\
        \midrule
        Overall Course of 2h & 90.09/0.04\footnotemark[9] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
        Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
        Teaching interval ($I_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
        Post-teaching interval ($I_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
        Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[10]/-2.68 & 120/2.96 \\
        \bottomrule
    \end{tabularx}
    \label{tab_1}

\begin{figure}[H]
  \centering
  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
  \label{fig.3}
\end{figure}

@@

Means, standard deviations, and range of teachers' unstandardized and
standardized HR for the entire study period, and for the five intervals,
are shown in Table \ref{tab_1}. Figure \ref{fig.3} displays the
unstandardized and standardized HR trends, respectively, over the course
of the entire study period. HR initially increased, peaked, and then
decreased, with the unstandardized and standardized HR graphs showing
high similarity. Thus, for all further analyses, we used participants'
standardized HR values.

@@

\begin{figure}[H]
  \centering
  \caption{Distribution of the standardized heart rate means in the five intervals}
  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
  \label{fig.4}
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
    \begin{tabularx}{\textwidth}{lccccc}
        \toprule
        Variable & Pre-teaching & Teaching & Post-teaching & Interview & End \\
        & interval & interval & interval & interval & interval \\
        \midrule
        Teaching Experience & $- .17/ - .27^*$ & .11/-.02 & $- .04/-.03$ & $.24^*/-.20$ & .04/.11 \\
        Disruption Appraisal & $- .01/.16$ & $- .20/.08$ & .20/$- .14$ & $- .13/.01$ & .04/.12 \\
        Confidence Appraisal & $- .10/ - .18$ & .06/.09 & .04/$- .03$ & .09/$- .19$ & $- .07/.13$ \\
        \bottomrule \\
          Note. * $p < .05$.
    \end{tabularx}
    \label{tab_3}
\end{table}

@@

@@

\begin{table}[ht]
    \centering
    \caption{Classification of nine, typical classroom disruptions according to @lohmann2003schulern performed in the micro-teaching unit by actors.}
    \begin{tabularx}{\textwidth}{XXX}
        \toprule
        \textbf{Verbal disruptions} & \textbf{Physical disruptions} & \textbf{Lack of eagerness to learn} \\
        \midrule
        Heckling & Clicking pen & Looking at phone \\
        Chatting & Snipping hands & Drawing \\
        Whispering & Drumming hands & Head on table \\
        \bottomrule
    \end{tabularx}
    \label{tab.a1}
\end{table}

\begin{figure}[htbp]
  \centering
  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
  \label{fig.a1}
\end{figure}

\begin{figure}[htbp]
  \centering\caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
  \label{fig.a2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
  \label{fig.a3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \label{fig.a4}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
  \label{fig.a5}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
  \label{fig.a6}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
  \label{fig.a7}
\end{figure}
